---
title: "Automated Variable Selection Experimental"
author: "SRC"
date: "Wednesday, June 10, 2015"
output: html_document
---

```{r ReadInFiles, echo=FALSE}
require(ggplot2)
require(stringr)
require(plyr)
require(Hmisc)
require(texreg)
options(error=recover)
# setwd("K:\\Development\\Competition")
setwd("C:\\Users\\Greg Sanders\\Documents\\Development\\Competition")
#setwd("C:/Users/scohen/My Documents/Competition/Competition/")
# Path<-"K:\\2007-01 PROFESSIONAL SERVICES\\R scripts and data\\"
Path<-"C:\\Users\\Greg Sanders\\SkyDrive\\Documents\\R Scripts and Data SkyDrive\\"
#path <- "C:/Users/scohen/My Documents/Competition/Competition/"

KOfflist  <- read.csv(
    paste("data\\defense_office_competition_combined.csv", sep = ""),
    header = TRUE, sep = ",", dec = ".", strip.white = TRUE, 
    na.strings = c("NULL","NA",""),
    stringsAsFactors = TRUE
    )

KOfflist <- KOfflist[KOfflist$Exclude == "FALSE", ] 
```

###Variable Selection Process

What we have done so far is **Forward Selection** which means we add each variable and check the descriptive statistics as each variable is added as well as check how it affects the other variables. 

This yields the model:

```{r echo=TRUE}

jfit1 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pAir + pWnA + pEnC + pIDV, data=KOfflist)

summary(jfit1)
```

**Criterion-based procedures**

The Akaike Information Criterion (AIC) and the Bayes Information Criterion (BIC) are criteria that avoid fitting all the models and instead only evaluate likely candidates.  

The criteria:

AIC = -2log - likelihood +2p

BIC = -2log - likelihood + plog*n

The AIC function does not evaluate the AIC for all possible models but uses a search method that compares models sequentially.  

Here I 

1.model the equation using about all the possible independent variables.

2. Use the AIC to select different models and show which has the lowest AIC. 
```{r echo=TRUE}
zfit <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ pAir+ pVessel+ pLand+ pMnS+ pWnA+ pEnC+ pFnC+ pIDV+ pFixed+ pCostPlus+ pIncentFee+ log(TotalCount)+ log(TotalValue), data=KOfflist) 

step(zfit)

AIC(zfit)

```

This model that yielded the lowest AIC and here is a comparison of the three models: 

1. zfit = all possible variables
2. yfit = the model suggested by AIC
3. jfit = the model we found using forward selection

``` {r echo=TRUE}
yfit <- lm(pEffectiveComp ~ pcService+ I(pcService^2) + pAir + pLand + pWnA + pFnC + pIDV + pFixed, data=KOfflist)


screenreg(list(zfit, yfit, jfit1))

```

[reference]{http://www.biostat.jhsph.edu/~iruczins/teaching/jf/ch10.pdf}

check this out: http://www.palgrave-journals.com/jt/journal/v18/n1/full/jt200926a.html 
