---
title: "Competition_Regression"
author: "Greg Sanders"
date: "Sunday, March 15, 2015"
output:
  html_document:
    keep_md: yes
---


```{r hiddensetup, echo = FALSE}
require(ggplot2)
require(stringr)
require(plyr)
require(Hmisc)
require(texreg)
options(error=recover)
setwd("K:\\Development\\Competition")
# setwd("C:\\Users\\Greg Sanders\\Documents\\Development\\Fixed-price")
#setwd("C:/Users/scohen/My Documents/Competition/Competition/")
Path<-"K:\\2007-01 PROFESSIONAL SERVICES\\R scripts and data\\"
# Path<-"C:\\Users\\Greg Sanders\\SkyDrive\\Documents\\R Scripts and Data SkyDrive\\"
#path <- "C:/Users/scohen/My Documents/Competition/Competition/"
source(paste(Path,"lookups.r",sep=""))
layout(matrix(c(1,2,3,4),2,2))
```


```{r setup}
MCClist  <- read.csv(
    paste("data\\defense_mcc_competition_combined.csv", sep = ""),
    header = TRUE, sep = ",", dec = ".", strip.white = TRUE, 
    na.strings = c("NULL","NA",""),
    stringsAsFactors = TRUE
    )

MCClist$TotalValue<-MCClist$TotalValue
MCClist<-subset(MCClist,!MajorCommandID %in% c("ORG-2841",
"ORG-2776",
"ORG-4793",
"ORG-2849",
"ORG-2762",
"ORG-4020",
"ORG-2840",
"ORG-2757")
)

ggplot(data=MCClist,aes(x=pEffectiveComp))+geom_bar()
ggplot(data=MCClist,aes(x=sqrt(pEffectiveComp)))+geom_bar()
ggplot(data=MCClist,aes(x=log1p(pEffectiveComp)))+geom_bar()


names(MCClist)

LMsummaryLine<-function(fit,Unit=NULL){
    data.frame(  Equation=as.character(summary(fit)$call)[2],
        Source=as.character(summary(fit)$call)[3],
           Slope=coefficients(fit)[2:length(coefficients(fit))],
           SlopeStdError=summary(fit)$coefficients[2:length(coefficients(fit)),2],
           Intercept=coefficients(fit)[1],         
           AdjRsquared=summary(fit)$adj.r.squared,
            Pvalue=coef(summary(fit))[2:length(coefficients(fit)),4]
           #anova(fit)$'Pr(>F)'[1]


           )
    #Source: http://stackoverflow.com/questions/5587676/pull-out-p-values-and-r-squared-from-a-linear-regression
    #http://stackoverflow.com/questions/23838937/extract-pvalue-from-glm
}

```

 Multiple Linear Regression Example 
 
```{r PSR}
#
# fit <- lm(y ~ x1 + x2 + x3, data=mydata)

rcorr(as.matrix(subset(MCClist,select=c(pProduct,pService,pRnD))))

ggplot(data=MCClist,aes(x=pAir))+geom_bar(bin=0.01)
ggplot(data=MCClist,aes(x=sqrt(pAir)))+geom_bar(bin=0.01)
ggplot(data=MCClist,aes(x=log1p(pAir)))+geom_bar(bin=0.01)



ggplot(data=MCClist,aes(x=pService,y=pEffectiveComp))+geom_point()
fita <- lm(pEffectiveComp ~ pService, data=MCClist)
summary(fita) 
dfPSR<-LMsummaryLine(fita)   
plot(fita)
MCClist$pcService<-MCClist$pService-0.5


ggplot(data=MCClist,aes(x=pcService,y=pEffectiveComp))+geom_point()
fitb <- lm(pEffectiveComp ~ pcService + I(pcService^2), data = MCClist)
summary(fitb) 
dfPSR<-LMsummaryLine(fitb)   
plot(fitb)


ggplot(data=MCClist,aes(x=pProduct,y=pEffectiveComp))+geom_point()
fitc <- lm(pEffectiveComp ~ pProduct, data=MCClist)
summary(fitc) 
sqdfPSR<-LMsummaryLine(fitc)   
plot(fitc)


ggplot(data=MCClist,aes(x=pRnD,y=pEffectiveComp))+geom_point()
MCClist$pRnD[MCClist$pRnD<0]<-0


ggplot(data=MCClist,aes(x=log1p(pRnD),y=pEffectiveComp))+geom_point()
fitd <- lm(pEffectiveComp ~ pcService + I(pcService^2) + sqrt(pRnD), data=MCClist)
summary(fitd) 
dfPSR<-LMsummaryLine(fitd)   
plot(fitd)
screenreg(list(fita, fitb, fitc, fitd))


View(dfPSR)
```

Because pProduct, pService, PRnD, and unlabeled data are mutually exhaustive


The minimum p-value is for the linear modpRnD but `r dfPSR$Pvalue[rownames(dfPSR)=="pRnD"]`. That's far too high to use, but worth a quick closer look in case theres something going on there we're missing.

Switching over to log of RnD is significantly more promising, but still doesn't reach significance. The log of pProduct and pService were also checked, but were not promising enough to merit further inclusion.


```{r Platform}

rcorr(as.matrix(subset(MCClist,select=c(pService,pRnD,pFnC,pAir,pVessel,pLand,pWnA,pMnS,pEnC))))
rcorr(cbind(MCClist$pFnC,MCClist$pService^2))
#Missiles and Space is highly correlated with RnD


#
# fit <- lm(y ~ x1 + x2 + x3, data=mydata)
ggplot(data=MCClist,aes(x=pAir,y=pEffectiveComp))+geom_point()
ggplot(data=MCClist,aes(x=sqrt(pAir),y=pEffectiveComp))+geom_point()
##EFFECTIVECOMP~SERVICE
fita <- lm(pEffectiveComp ~ pService, data=MCClist)
fitb <- lm(pEffectiveComp ~ pcService + I(pcService^2), data=MCClist)
fitd <- lm(pEffectiveComp ~ pcService + I(pcService^2) + pRnD, data=MCClist)
fite <- lm(pEffectiveComp ~ pcService + I(pcService^2) + pRnD+ sqrt(pRnD), data=MCClist)
afit <- lm(pEffectiveComp ~ pcService+I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir, data=MCClist)
summary(fite)
summary(afit) 
dfMCC<-LMsummaryLine(afit)
plot(afit)
screenreg(list(fita, fitb, fitd, fite, afit))
##sqrt(pRnD) increases R^2 and the significance of pcService
##pAir increases R^2, decreases significance of pcService but increases value and significance of pcservice^2 pvalue(.0114 to .0082)

bfit <- lm(pEffectiveComp ~ pcService+I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir+sqrt(pAir), data=MCClist)  
summary(bfit) 
dfMCC<-LMsummaryLine(bfit)
plot(bfit)

screenreg(list(fita, fitb, fitd, fite, afit, bfit))
##adding sqrt(pAir) does not change any of the descirptive statistics, it decreases the coefficient on psdrvice^2 by .003. R^2 does not change.  Thus it should not be further included 

```


```{r pVessel}
ggplot(data=MCClist,aes(x=pVessel,y=pEffectiveComp))+geom_point()
ggplot(data=MCClist,aes(x=sqrt(pVessel),y=pEffectiveComp))+geom_point()

ggplot(data=MCClist,aes(x=pVessel))+geom_bar(bin=0.01)
ggplot(data=MCClist,aes(x=sqrt(pVessel)))+geom_bar(bin=0.01)
ggplot(data=MCClist,aes(x=log1p(pVessel)))+geom_bar(bin=0.01)

##EFFECTIVECOMP~Product +vessel
#Sqrt doesn't seem to illuminate much
fitc <- lm(pEffectiveComp ~ pProduct, data=MCClist)
fit5 <- lm(pEffectiveComp ~ pProduct+ pRnD, data=MCClist)
fit6 <- lm(pEffectiveComp ~ pProduct+ pRnD+ sqrt(pRnD), data=MCClist)
fit7 <- lm(pEffectiveComp ~ pProduct+ pRnD+ sqrt(pRnD)+ pAir, data=MCClist)
fit1 <- lm(pEffectiveComp ~ pProduct+ pRnD+ sqrt(pRnD)+ pAir+ pVessel, data=MCClist)
summary(fitc)
summary(fit6)
summary(fit7)
summary(fit1) 
dfMCC<-rbind(dfMCC,LMsummaryLine(fit1))
screenreg(list(fitc, fit5, fit6, fit7, fit1))
##air and vessel do not do not change descriptive statistics to any meaningful extent and are not significant. 

##effectivecomp ~service + vessel
afit <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir, data=MCClist) 
fit2 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir+ pVessel, data=MCClist)
fit8 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir+ pVessel+ sqrt(pVessel), data=MCClist)
fit4 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir+ pVessel+ sqrt(pVessel), data=MCClist[rownames(MCClist)!=58,])
summary(afit)
summary(fit2)
summary(fit8)
summary(fit4)
screenreg(list(afit, fit2, fit8, fit4))
##vessel is not significant, nor sqrt(vessel) nor when outliers are removed, and doesn't affect descriptive statistics of the model or other variables, thus it should not be included.  

summary(fit2) 
dfMCC<-LMsummaryLine(fit2)
plot(fit2)

# #fit3 <- lm(pEffectiveComp ~ pcService+I(pcService^2)+ sqrt(pRnD)+ pAir +pVessel, data=MCClist)
# summary(fit3) 
# dfMCC<-LMsummaryLine(fit3)
# plot(fit3)
# screenreg(list(fit1, fit2, fit3))

##fit4 <- lm(pEffectiveComp ~ pcService+I(pcService^2)+ sqrt(pRnD)+ pAir +pVessel,
          #data=MCClist[rownames(MCClist)!=58,])
summary(fit4) 
dfMCC<-LMsummaryLine(fit4)
plot(fit4)
#screenreg(list(fit1, fit2, fit3, fit4))


```



```{r pLand}
#Slight reduction in R-Squared


ggplot(data=MCClist,aes(x=pLand,y=pEffectiveComp))+geom_point()
ggplot(data=MCClist,aes(x=sqrt(pLand),y=pEffectiveComp))+geom_point()
ggplot(data=MCClist,aes(x=log1p(pLand),y=pEffectiveComp))+geom_point()
ggplot(data=MCClist,aes(x=pLand,y=pEffectiveComp))+geom_point()

bfit <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir, data=MCClist)  
afit1 <- lm(pEffectiveComp ~ pcService+I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir+ pLand, data=MCClist)
summary(bfit)
summary(afit1) 
dfMCC<-LMsummaryLine(afit1)
plot(afit1)
screenreg(list(bfit, afit1))
##adding land does not change any coefficients or descriptive statistics and pair is not statistically significant 

afit2 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir+ sqrt(pAir)+ pLand+ sqrt(pLand), data=MCClist)
summary(afit2) 
dfMCC<-LMsummaryLine(afit2)
plot(afit2)
screenreg(list(bfit, afit1, afit2))
##sqrt(pland) does not change any descriptive statistics and is not statistically significant 

```

Land vehicles has a smaller competitive than other platforms, but it still should be negative, so we'll leave it out. Also, Land does not improve the model (r squared does not change) neither is it significant (p=.77 for land and .7 for sqrtland)

```{r MnS}

ggplot(data=MCClist,aes(x=pMnS,y=pEffectiveComp))+geom_point()
ggplot(data=MCClist,aes(x=sqrt(pMnS),y=pEffectiveComp))+geom_point()

bfit <- lm(pEffectiveComp ~ pcService+I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir, data=MCClist)  

bfit1 <- lm(pEffectiveComp ~ pcService+I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir+ pMnS, data=MCClist)
summary(bfit1) 

bfit2 <- lm(pEffectiveComp ~ pcService+I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir+ pMnS+ pVessel, data=MCClist)

#bfit2 <- lm(pEffectiveComp ~ pcService+I(pcService^2)+ pAir + pMnS, data=MCClist)
summary(bfit)
summary(bfit1)
plot(bfit2)
screenreg(list(bfit, bfit1))
##pMns increases the r^2 from .38 to .42, is significant at the 90% level (p=.0569), increases the p value for pcservice^2 by .003 and increases the significance of pRnD and sqrt(pRnD) to the 90% level.   

bfit3 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir, data=subset(MCClist,                                                                                    rownames(MCClist)!=58))
summary(bfit3) 
plot(bfit3)

bfit4 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir + pMnS, data=subset(MCClist,                                                                                    rownames(MCClist)!=58))
summary(bfit4)

bfit5 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir+ pMnS+ pVessel, data=subset(MCClist,                                                                                    rownames(MCClist)!=58))
summary(bfit5)
screenreg(list(bfit, bfit1, bfit2, bfit3, bfit4, bfit5))

##pMnS increases signifiance when pVessel is added when eliminating the outlier.  the coefficient of pcService^2 decreases by .05 when the outlier is removed.  The r^2 between model with outlier and model without does not change.  comparing the models with and without the outlier when pvessel, there is not much difference.  The biggest change to note here is the increase in significance of pMnS when accounting for the outlier and adding pVessel 
```

**talk this over after looking at the models from the previous section**
Due to the correlation betwen pMnS and pRnD (.59), it risks multicollinearity to have them both in the same plot, *but since .59 is less than .9 this should not cause any problems*. Happily, MnS appears has the correct sign and a lower p-value than sqrt(RnD) which also eliminates the difficult to interpret square roots. Trading them appears to be a positive exchange. Land briefly showed the wrong sign, but upon removing entry 11, that problem was eliminated. However, adding vessel back in without entry 58 still leaves vessel with a positive sign. *talk about notes that I wrote in the r sections* 

```{r pWnA}


ggplot(data=MCClist,aes(x=pWnA,y=pEffectiveComp))+geom_point()
ggplot(data=MCClist,aes(x=sqrt(pWnA),y=pEffectiveComp))+geom_point()

cfit1 <- lm(pEffectiveComp ~ pcService+I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir+ pMnS, data=MCClist) 

cfit3 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir+ pWnA, data=MCClist)

cfit2 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir + pMnS +pWnA, data=MCClist)
summary(cfit1)
summary(cfit3)
summary(cfit2)
screenreg(list(cfit1, cfit3, cfit2))

##adding pWnA decreases the significance of pMnS.  Also, adding pWnA increases r^2 by .06.  Thus, including pMnS from now on should be discussed.  For now, I'm goign to not include it but it can always be added in if this logic is not sufficient. 

# cfit1 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pAir + pMnS, data=MCClist)
# summary(cfit1) 
# plot(cfit1)
# 
# cfit2 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pAir + pMnS +pWnA, data=MCClist)
# 
# cfit3 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pAir+ pWnA, data=MCClist)
# summary(cfit3)
# summary(cfit2)
# dfMCC<-rbind(dfMCC,LMsummaryLine(cfit1))

#screenreg(list(cfit1, cfit3, cfit2))

```

pWnA is very siginificant (p=.005) and increases the r^2 of the model (.39->.46).  pMnS is kept in the first two models here to see if it changes at all with the addition of pWnA, since it doesn't, it will still be removed.  

```{r ElectronicAndCommunications}

ggplot(data=MCClist,aes(x=pEnC,y=pEffectiveComp))+geom_point()
ggplot(data=MCClist,aes(x=sqrt(pEnC),y=pEffectiveComp))+geom_point()
ggplot(data=MCClist,aes(x=log1p(pEnC),y=pEffectiveComp))+geom_point()

dfit1 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pAir+ pRnD+ sqrt(pRnD)+ pWnA, data=MCClist)
summary(dfit1) 
plot(dfit1)

dfit2 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pAir+ pRnD+ sqrt(pRnD)+ pWnA+ pEnC, data=MCClist)
summary(dfit2) 
plot(dfit2)
screenreg(list(dfit1, dfit2))

dfit3 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pAir+ pRnD+ sqrt(pRnD)+ pWnA +pEnC +pVessel, data=subset(MCClist, rownames(MCClist)!=58 ))
summary(dfit3) 
plot(dfit3)
screenreg(list(dfit1, dfit2, dfit3))

##adding pEnC does not influence r^2 significantly and it decreases the significance of pcService^2.  It is also not significant.  When looked at with vessel and removing the outlier, neither pEnC or pVessel is significant, the r^2 does not change and the significance of pcService^2 is significant at the 95% level.  Thus, pEnC shoudl not be included.  
```

**relook at this**-->
pcService was dropped because its p-value reached one(*I don't see this*), after the addition of Electronics and Communications it provided no additional information. Unfortunately attempts to reintroduce vessel or land were unsuccessful as the sign was still postive.


```{r FacilityAndConstruction}

ggplot(data=MCClist,aes(x=pFnC,y=pEffectiveComp))+geom_point()
ggplot(data=MCClist,aes(x=sqrt(pFnC),y=pEffectiveComp))+geom_point()
ggplot(data=MCClist,aes(x=log1p(pFnC),y=pEffectiveComp))+geom_point()




efit1 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pAir+ pRnD+ sqrt(pRnD)+ pWnA, data=MCClist)
summary(efit1) 
plot(efit1)

efit2 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pAir + pRnD+ sqrt(pRnD)+ pWnA + pFnC, data=MCClist)
summary(efit2) 
plot(efit2)
screenreg(list(efit1, efit2))

efit3 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pAir+ pRnD+ sqrt(pRnD)+ +pWnA + pFnC+ pVessel, data=MCClist)
summary(efit3) 
plot(efit3)
screenreg(list(efit1, efit2, efit3))

efit4 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pAir+ pRnD+ sqrt(pRnD)+ pWnA + pFnC+ pVessel, data=subset(MCClist, rownames(MCClist)!=58 & rownames(MCClist)!=59 ))
summary(efit4) 
plot(efit4)
screenreg(list(efit1, efit2, efit3, efit4))

##the addition of pFnC increases r^2 by .02, increases coefficients pcService^2 by .05, decreases the significance of sqrt(pRnD) and does not change the other variables significantly.  when vessel is added, r^2 does not change, and neither do any other coefficients to a large extent.  When the outlier is eliminated, the sign of pVessel changes to positive and increases by .51, however, it is not significant (p=.376).  thus, I do not think pFnC should continue as part of the model.  
```


The remaining platform portfolios: Other R&D, other products, and other services were not included in this analysis as the type of they either do not support a particular platform or said support is uncategorized. As a result they add little information to that already available through pProduct, pService, and pRnD

```{r IDV}
rcorr(as.matrix(subset(MCClist,select=c(pService,pRnD,pAir,pLand,pWnA,pMnS,pEnC,pIDV,pFixed,pCostPlus,pIncentFee))))


ggplot(data=MCClist,aes(x=pIDV,y=pEffectiveComp))+geom_point()

ffit1 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir + pWnA, data=MCClist)
summary(ffit1) 
plot(ffit1)

ffit2 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir + pWnA + pIDV, data=MCClist)
           
summary(ffit2) 
dfMCC<-rbind(dfMCC,LMsummaryLine(fit))
plot(ffit2)
screenreg(list(ffit1, ffit2))
##pIdv increases r^2 by .04, increases the coefficient of pcService^2 by .02, maintains statistically significant coefficients of the other variables and is itself statistically significant at the 90% level, thus IDV should be included in the model.  
```

IDV is a solid new addition, statistically significant in its own right.





```{r FixedPrice}
ggplot(data=MCClist,aes(x=pFixed,y=pEffectiveComp))+geom_point()

gfit2 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir + pWnA + pIDV, data=MCClist)

gfit1 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir+ pWnA+ pIDV+ pFixed, data=MCClist)
summary(gfit1) 
dfMCC<-rbind(dfMCC,LMsummaryLine(gfit1))
plot(gfit1)
screenreg(list(gfit2, gfit1))

##With the addition of pFixed, the r^2 increases by .01, the coefficient of pcService does not change and pFixed is not statistically significant.  Thus, pFixed should not be included further on. 

```

Fixed-price does does not subtsantially add to the model when compared to PMnS and pWnA which it replaces. The sign also does not align with expectations, given that fixed-price contracts place greater risk on the vendor.

```{r CostPluse}
ggplot(data=MCClist,aes(x=pFixed,y=pEffectiveComp))+geom_point()

hfit1 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir + pWnA + pIDV, data=MCClist)

summary(hfit1) 
dfMCC<-rbind(dfMCC,LMsummaryLine(hfit1))
plot(hfit1)

hfit2 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir + pWnA + pIDV+pCostPlus, data=subset(MCClist,!rownames(MCClist) %in% c(59) ))
summary(hfit2) 
dfMCC<-rbind(dfMCC,LMsummaryLine(hfit2))
plot(hfit2)
screenreg(list(hfit1, hfit2))
##pCost plus also does not change any of the descriptive statistics very signficantly and itself is not statistically significant. 
```

similarly, pCostPlus does not add to the model versus the correlating variables it replaces.


```{r IncentiveFee}

ifit1 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir + pWnA + pIDV, data=MCClist)
summary(ifit1) 
plot(ifit1)

ifit2 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir + pWnA + pIDV+ pIncentFee, data=MCClist)

summary(ifit2) 
plot(ifit2)
screenreg(list(ifit1, ifit2))

##the addition of incentive fee into the model does not change any of the coefficients of the other variables to a meaningful extent and does not change the r^2 value, thus it will not be continued in the model.  

```

The study team had expected incentive fee contracts to increase competition. In addition, it has an abysmal p-value, so it will not be added to the model.









```{r TotalCount}

rcorr(as.matrix(subset(MCClist,select=c(pService,pRnD,pAir,pLand,pWnA,pMnS,pEnC,pIDV,TotalCount,TotalValue,avSize))))

ggplot(data=MCClist,aes(x=TotalCount))+geom_bar()
ggplot(data=MCClist,aes(x=log(TotalCount)))+geom_bar()
ggplot(data=MCClist,aes(x=TotalCount,y=pEffectiveComp))+geom_point()
ggplot(data=MCClist,aes(x=log(TotalCount),y=pEffectiveComp))+geom_point()

jfit1 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir + pWnA + pIDV, data=MCClist)
summary(jfit1)
plot(jfit1)


ggplot(data=MCClist,aes(x=TotalCount))+geom_bar()
ggplot(data=MCClist,aes(x=log(TotalCount)))+geom_bar()
ggplot(data=MCClist,aes(x=TotalCount,y=pEffectiveComp))+geom_point()
ggplot(data=MCClist,aes(x=log(TotalCount),y=pEffectiveComp))+geom_point()

jfit2 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir + pWnA + pIDV+ TotalCount, data=MCClist)
summary(jfit2)
plot(jfit2)

jfit3 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir + pWnA + pIDV+ TotalCount+ log(TotalCount), data=MCClist)


jfit4 <- lm(pEffectiveComp ~ pcService+ I(pcService^2)+ pRnD+ sqrt(pRnD)+ pAir + pWnA + pIDV+ TotalCount+ log(TotalCount), datadata=subset(MCClist,!rownames(MCClist) %in% c(10,12.56,58,59) ))=MCClist)

screenreg(list(jfit1, jfit2, jfit3))


# jfit3 <- lm(pEffectiveComp ~ I(pcService^2)+ pAir + pMnS  +pWnA+pEnC +pFnC +pIDV+log(TotalCount)+pVessel+pVessel:I(pcService^2), data=subset(MCClist,
#                                                                                                !rownames(MCClist) %in% c(10,12.56,58,59) ))
# summary(jfit3)
# plot(jfit3)

##total count does not change the model in anyway, and it's interesting to note that its coefficients are zero.

```

SRCstopped
*samantha comment:* I'm not sure what you are doing here:
```{r TotalValue}

rcorr(as.matrix(subset(MCClist,select=c(pService,pRnD,pAir,pLand,pWnA,pMnS,pEnC,pIDV,TotalCount,TotalValue,avSize))))

ggplot(data=MCClist,aes(x=TotalValue))+geom_bar()
ggplot(data=MCClist,aes(x=log(TotalValue)))+geom_bar()
ggplot(data=MCClist,aes(x=TotalValue,y=pEffectiveComp))+geom_point()
ggplot(data=MCClist,aes(x=log(TotalValue),y=pEffectiveComp))+geom_point()
kfit1 <- lm(pEffectiveComp ~ I(pcService^2)+ pAir + pMnS  +pWnA+pEnC +pFnC +pIDV+log(TotalValue), data=MCClist)
summary(kfit1)
plot(kfit1)

kfit2 <- lm(pEffectiveComp ~ I(pcService^2)+ pAir + pFnC  +pWnA+pEnC +pIDV+log(TotalValue) + log(TotalValue):I(pcService^2), data=subset(MCClist,
                                                                                     rownames(MCClist)!=26))
summary(kfit2)
plot(kfit2)

kfit3 <- lm(pEffectiveComp ~ pLand+pAir + pFnC  +pWnA+pEnC +pIDV+log(TotalValue), data=subset(MCClist,
                                                                                     rownames(MCClist)!=26))
summary(kfit3)
plot(kfit3)

kfit4 <- lm(pEffectiveComp ~ pVessel+pAir + pFnC  +pWnA+pEnC +pIDV+log(TotalValue), data=subset(MCClist,
                                                                                     rownames(MCClist)!=26&
                                                                                         rownames(MCClist)!=58))
summary(kfit4)
plot(kfit4)

kfit5 <- lm(pEffectiveComp ~ pMnS+pAir + pFnC  +pWnA+pEnC +pIDV+log(TotalValue), data=subset(MCClist,
                                                                                     rownames(MCClist)!=26))
summary(kfit5)
plot(kfit5)
screenreg(list(kfit1, kfit2, kfit3, kfit4, kfit5))

```



```{r AverageSize}


lfit1 <- lm(pEffectiveComp ~ I(pcService^2)+ pAir  +pMnS +pWnA +pEnC +pFnC +pIDV +avSize, data=MCClist)
summary(lfit1) 
plot(lfit1)


lfit2 <- lm(pEffectiveComp ~ I(pcService^2)+ pAir  +pMnS +pWnA +pEnC +pFnC +pIDV +lavSize, data=MCClist)
summary(lfit2) 
plot(lfit2)

rcorr(as.matrix(subset(MCClist,select=c(pService,pRnD,pAir,pLand,pWnA,pMnS,pEnC,pIDV,TotalCount,TotalValue,avSize))))

ggplot(data=MCClist,aes(x=avSize))+geom_bar()
ggplot(data=MCClist,aes(x=log(avSize)))+geom_bar()
ggplot(data=MCClist,aes(x=avSize,y=pEffectiveComp))+geom_point()
ggplot(data=MCClist,aes(x=log(avSize),y=pEffectiveComp))+geom_point()
lfit3 <- lm(pEffectiveComp ~ I(pcService^2)+ pAir + pLand  +log(avSize)  +pWnA+pEnC +pIDV+log(TotalCount), data=subset(MCClist,
                                                                                     rownames(MCClist)!=26))
summary(lfit3)
plot(lfit3)


lfit4 <- lm(pEffectiveComp ~ I(pcService^2)+ pAir + pLand  +log(avSize)  +pWnA+pEnC +pIDV+log(TotalCount) +pRnD, data=subset(MCClist,
                                                                                     rownames(MCClist)!=26))
summary(lfit4)
plot(lfit4)






lfit5 <- lm(pEffectiveComp ~ I(pcService^2)+ pAir + pLand  +log(avSize)  +pWnA+pEnC +pIDV+log(TotalCount) +pRnD +pVessel, data=subset(MCClist,
                                                                                     rownames(MCClist)!=26 &
              rownames(MCClist)!=59))
summary(lfit5)
plot(lfit5)


lfit6 <- lm(log1p(pEffectiveComp) ~ I(pcService^2)+ pAir + pLand  +log(avSize)  +pWnA+pEnC +pIDV+log(TotalCount) +pRnD, data=subset(MCClist,
                                                                                     rownames(MCClist)!=26 &
              rownames(MCClist)!=59))
summary(lfit6)
plot(lfit6)


lfit7 <- lm(pEffectiveComp ~ I(pcService^2)+ pAir  +pMnS +pWnA +pEnC  +pIDV +pIDV:I(pcService^2), data=MCClist)
summary(lfit7) 
plot(lfit7)


lfit8 <- lm(pEffectiveComp ~ I(pcService^2)+ pAir  +pMnS +pWnA +pEnC  +pIDV +pIDV:I(pcService^2)+pIDV:pcService +pcService, data=MCClist)
summary(lfit8) 
plot(lfit8)
screenreg(list(lfit1, lfit2, lfit3, lfit4, lfit5, lfit6, lfit7, lfit8))

```


```{r StateValidation}
mfit1 <- lm(pEffectiveComp ~ pService:pProduct+ pAir  +pMnS +pWnA +pEnC  +pIDV +pService +pService:pIDV +pProduct:pService:pIDV, data=MCClist)
summary(mfit1) 
plot(mfit1)


StateList  <- read.csv(
    paste("data\\defense_state_competition_combined.csv", sep = ""),
    header = TRUE, sep = ",", dec = ".", strip.white = TRUE, 
    na.strings = c("NULL","NA",""),
    stringsAsFactors = TRUE
    )
names(StateList)

StateList <-subset(StateList ,!PoPstateCode %in% c("VI",
"AS",
"MP",
"AE",
"PW",
"US",
"UK",
"GM",
"GB",
"JA",
"ON",
"QC",
"   ",
"BC"))

rcorr(as.matrix(subset(StateList,select=c(pService,pProduct,pRnD,pAir,pLand,pVessel,pWnA,pFnC,pMnS,pEnC,pIDV,pFixed,pCostPlus,TotalCount,TotalValue,avSize))))

StateList$pcService<-StateList$pService-0.5
mfit2 <- lm(pEffectiveComp ~ I(pcService^2)+ pAir  +pMnS +pWnA +pEnC  +pIDV +pIDV:I(pcService^2)+pIDV:pcService +pcService, data=StateList)
summary(mfit2) 
plot(mfit2)


mfit3 <- lm(pEffectiveComp ~  pLand +pMnS +pWnA +pEnC  +pIDV +pService, data=StateList)
summary(fit) 
plot(fit)



mfit4 <- lm(pEffectiveComp ~  pAir  +pMnS +pWnA +pWnA:pProduct+pEnC  +pIDV  +pProduct, data=StateList)
summary(mfit4) 
plot(mfit4)


mfit5 <- lm(pEffectiveComp ~  pAir  +pMnS +pWnA +pWnA:pIDV+pEnC  +pIDV  +pProduct, data=StateList)
summary(mfit5) 
plot(mfit5)

mfit6 <- lm(pEffectiveComp ~  pAir  +pMnS +pEnC +pIDV +pProduct, data=StateList)
summary(mfit6) 
plot(mfit6)

mfit7 <- lm(pEffectiveComp ~  pAir  +pMnS +pEnC +pIDV+ pVessel+pProduct, data=StateList)
summary(mfit7) 
plot(mfit7)


mfit8 <- lm(pEffectiveComp ~  pAir  +pMnS +pEnC +pIDV+ pVessel+pProduct+pEnC:pProduct, data=StateList)
summary(mfit8) 
plot(mfit8)


mfit9 <- lm(pEffectiveComp ~  pAir  +pMnS +pEnC +pIDV+ pVessel+pProduct +lavSize, data=StateList)
summary(mfit9) 
plot(mfit9)


mfit10 <- lm(pEffectiveComp ~  pAir  +pMnS +pWnA +pEnC +pLand +pVessel + pIDV +pService, data=StateList)
summary(mfit10) 
plot(mfit10)
screenreg(list(mfit1, mfit2, mfit3, mfit4, mfit5, mfit6, mfit7, mfit8, mfit9, mfit10))



```
