---
title: "MCClist regression"
author: "src"
date: "July 14, 2015"
output: html_document
---

Variables to test with Effective competition: 

**platforms**

-Services
-Weapons and Ammunition
-Electronics and Communication
-Indefinite Delivery Vehicle
-Land Vehicles
-Aircraft and Drones
-Missiles and space
-Ships and Submarines

**category unknown**

-Fixed Price Contracts
-Indefinite Delivery Vehicle Multi-Award Contracts
-Indefinite Delivery Vehicle Single-Award Contracts

**Product Service Codes**

-Aircraft
-Land
-Missiles and Space
-Engines and Power plants
-Ships 
-Facilities Related Services and Construction
-Professional, Administrative and Management Support
-Other

**Load packages and data:**

``` {r echo=TRUE}

require(ggplot2)
require(stringr)
require(plyr)
require(Hmisc)
require(texreg)
options(error=recover)
setwd("K:\\Development\\Competition")
# setwd("C:\\Users\\Greg Sanders\\Documents\\Development\\Fixed-price")
#setwd("C:/Users/scohen/My Documents/Competition/Competition/")
Path<-"K:\\2007-01 PROFESSIONAL SERVICES\\R scripts and data\\"
# Path<-"C:\\Users\\Greg Sanders\\SkyDrive\\Documents\\R Scripts and Data SkyDrive\\"
#path <- "C:/Users/scohen/My Documents/Competition/Competition/"
source(paste(Path,"lookups.r",sep=""))
layout(matrix(c(1,2,3,4),2,2))

MCClist  <- read.csv(
    paste("data\\defense_mcc_competition_combined_2000-2013.csv", sep = ""),
    header = TRUE, sep = ",", dec = ".", strip.white = TRUE, 
    na.strings = c("NULL","NA",""),
    stringsAsFactors = TRUE
    )

MCClist$TotalValue<-MCClist$TotalValue
MCClist<-subset(MCClist,!MajorCommandID %in% c("ORG-2841",
"ORG-2776",
"ORG-4793",
"ORG-2849",
"ORG-2762",
"ORG-4020",
"ORG-2840",
"ORG-2757")
)


```


**Correlations of Variables**

``` {r echo=TRUE}

rcorr(as.matrix(subset(MCClist,select=c(pPSRServices,pPSRProducts, pPlatWnA, pPlatEnC, pIDV, pPlatLand, pPlatAir, pPlatMnS, pPlatVessel, pPlatOther, pRnD, pPriceFixed, pVehMAC, pVehSAC, pPscAir, pPscLand, pPscMnS, pPscEngines, pPscShips, pPscFRSnC, pPscPAMS, pPscOther))))

rcorr(as.matrix(subset(MCClist, select=c(pPSRServices, pIDV, pVehSAC))))

rcorr(as.matrix(subset(MCClist, select=c(pPSRServices, pPscFRSnC, pPscPAMS))))

rcorr(as.matrix(subset(MCClist, select=c(pIDV, pVehSAC))))

```

**Regressions**

Services:

``` {r echo=TRUE}

modela <- lm(pEffComp ~ pPSRServices, data = MCClist)
summary(modela)

screenreg(list(modela))

modelaa <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2), data = MCClist)
summary(modelaa)

screenreg(list(modela, modelaa))
```
**Observations** pPSRServices is not statistically significant and only influences the model by 1% (r^2 = .01) thus, it will not be included in the model. 

Products:

``` {r echo=TRUE}

modelb <- lm(pEffComp ~ pPSRProducts, data = MCClist)
summary(modelb)

screenreg(list(modelb))

```
**observations** not statistically significant and r^2 = .01

weapons and Ammunition Platform:

``` {r echo=TRUE}

modelc <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA, data = MCClist)
summary(modelc)

screenreg(list(modelaa,modelc))

```
**obersvations** pPlatWnA is statistically significant, adjusted r^2=.34, it will be included in the model for now but it's scatterplot does not look like it would have such an effect... 

**Electronics and Communication platform:**

``` {r echo=TRUE}

modeld <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pPlatEnC, data = MCClist)
summary(modeld)

screenreg(list(modelaa, modelc, modeld))

```
**Observations** EnC is not significant, does not affect anything meaningfully, with the exception of a boost to the significance of pPlatWnA, will not be included.

**IDV platform:**

``` {r echo=TRUE}

modele <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pIDV, data = MCClist)
summary(modele)

screenreg(list(modelaa, modelc, modele))


```
**Observations:** IDV is statistically significant at the 95% level. It increased adjusted r^2 by .04. Will be included in the model.



**Land Vehicles platform**
``` {r echo=TRUE}

modelf <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pIDV+ pPlatLand, data = MCClist)
summary(modelf)

screenreg(list(modelaa, modelc, modele, modelf))

```
**Observations** pPlatLand's scatterplot does not give any indication that there would be a statistically significant relationship, there are a few outliers that bring the relationship further than 10% contracts obligated and it's impact in the model is not very significant, and it's p value = .0933, thus it will not be included in the model. 

**Aircraft and Drones platform** 

``` {r echo=TRUE}

modelg <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pIDV+ pPlatAir, data = MCClist)
summary(modelg)

screenreg(list(modelaa, modelc, modele, modelg))

```
**Observations:** pPlatAir is statistically significant at the 99% level,  increases adjusted r^2 by .08. Will be included in the model. 

**Missiles and Space Platform**

``` {r echo=TRUE}

modelh <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pIDV+ pPlatAir+ pPlatMnS, data = MCClist)
summary(modelh)

screenreg(list(modelaa, modelc, modele, modelg, modelh))


```
**Observations:** Missiles and Space platform is not statisticaly significant, minimal changes to other cofeficients and does not affect r^2 (except decreases by .01), MnS will not be included

**Ships and Submarines Platform**

``` {r echo=TRUE}

modeli <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pIDV+ pPlatAir+ pPlatVessel, data = MCClist)
summary(modeli)

screenreg(list(modelaa, modelc, modele, modelg, modeli))

```
**Observations** Ships is not statistically significant, it do es not change r^2, and it doesn't really affect the other variables in the model. It will not be included. 

**Other Platforms**

``` {r echo=TRUE}

modelj <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pIDV+ pPlatAir+ pPlatOther, data = MCClist)
summary(modelj)

screenreg(list(modelaa, modelc, modele, modelg, modelj))

```
**Observations:** Other platform does is not significant, only results in a 0.01 change in r^2 and increases doesn't affect other coefficients in the model by very much and Will not be included in the model. 

**Research and Development** 

``` {r echo=TRUE}
modelk <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pIDV+ pPlatAir+ pRnD, data = MCClist)
summary(modelk)

screenreg(list(modelaa, modelc, modele, modelg, modelk))

```
**Observations** RnD is not statistically significant, does not change r^2 with a negative change to adjusted and decreases significance of other variables in the model, RnD will not be included 


**Fixed Price Contracts**

``` {r echo=TRUE}

modell <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pIDV+ pPlatAir+ pPriceFixed, data = MCClist)
summary(modell)

screenreg(list(modelaa, modelc, modele, modelg, modell))

```
**Observations** Fixed price is not statistically significant, does not affect adjusted r^2, it will not be included in the model

**Indefinite Delivery Vehicle Multi-award contracts**

``` {r echo=TRUE}

modelm <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pIDV+ pPlatAir+ pVehMAC, data = MCClist)
summary(modelm)

screenreg(list(modelaa, modelc, modele, modelg, modelm))

```
**Observations** IDV MAC is not statistically significant, it does change r^2 by 0.02, it has mixed effects on other variables, increasing the significance of pPSRServices^2 and decreasing the significance of pPlatWnA. It will not be included in the model. 

**IDV single-award contracts** 

``` {r echo=TRUE}

modeln <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pIDV+ pPlatAir+ pVehSAC, data = MCClist)
summary(modeln)

screenreg(list(modelaa, modelc, modele, modelg, modeln))

```
**Observations** IDV SAC is not statistically significant but it increases adjusted r^2 by .02 and  will be included in the model. 


**PSC Air**

``` {r echo=TRUE}

modelo <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pIDV+ pPlatAir+ pVehSAC+ pPscAir, data = MCClist)
summary(modelo)

screenreg(list(modelaa, modelc, modele, modelg, modeln, modelo))

```
**Observations**PSC air is not statistically significant and it does not affect the other coefficients of the model by very much. It does not change adjusted r^2. it will not be included in the model. 

**PSC land**

``` {r echo=TRUE}

modelp <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pIDV+ pPlatAir+ pVehSAC+ pPscLand, data = MCClist)
summary(modelp)

screenreg(list(modelaa, modelc, modele, modelg, modeln, modelp))

```
**Observations** PSC land is not statistically significant, due to its scatterplot, it will not be included in the model. The scatterplot has no indication of a statistically significant realionship. 

**PSC missiles and space**

``` {r echo=TRUE}

modelq <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pIDV+ pPlatAir+ pVehSAC+ pPscMnS, data = MCClist)
summary(modelq)

screenreg(list(modelaa, modelc, modele, modelg, modeln, modelq))

```
**Observations** MnS is not statistically significant, does not affect the other variables in a manner that increases significance and doesnt affect adjusted r^2, psc MnS will not be included in the model. Also it's scatter plot suggests this is all true. 

**PSC Enginges and Power Plants**

``` {r echo=TRUE}

modelr <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pIDV+ pPlatAir+ pVehSAC+ pPscEngines, data = MCClist)
summary(modelr)

screenreg(list(modelaa, modelc, modele, modelg, modeln, modelr))

```
**Observations** Engines is not statistically si gnificant nor does it change the other variables in a meaningful way and it's scatterplot suggests this. It will not be included in the model. 

**Psc Ships**

``` {r echo = TRUE}

models <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pIDV+ pPlatAir+ pVehSAC+ pPscShips, data = MCClist)
summary(models)

screenreg(list(modelaa, modelc, modele, modelg, modeln, models))

```
**Observations** psc ships is not significant and does not affect other aspects of the model, will not be included. 

**Facilities Related Services and Construction**

``` {r echo = TRUE}

modelt <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pIDV+ pPlatAir+ pVehSAC+ pPscFRSnC, data = MCClist)
summary(modelt)

screenreg(list(modelaa, modelc, modele, modelg, modeln, modelt))

```
**Observations:** FRSnC is not statistically statistically significant, does not change the other aspects of the model by very much, WnA decreases by .08, PSRservices by .06, Air by .01 and its does not affect r^2 or adjusted r^2 by mroe than .01, it will not be included in the model. 

**PAMS**

``` {r echo=TRUE}

modelu <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pIDV+ pPlatAir+ pVehSAC+ pPscPAMS, data = MCClist)
summary(modelu)

screenreg(list(modelaa, modelc, modele, modelg, modeln, modelu))

```
**Observations** pPscPAMS is not statistically significant, it doesn't affect other variables by more than .04 and doesn't affect r^2 by more than .01. It will not be included in the model. 

**PsC Other**

``` {r echo=TRUE}

modelv <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pIDV+ pPlatAir+ pVehSAC+ pPscOther, data = MCClist)
summary(modelv)

screenreg(list(modelaa, modelc, modele, modelg, modeln, modelv))

```
**Observations:** PSC other does not affect model and is not significant. will not be included in the model. 

Final Model:

``` {r echo=TRUE}

modelz <- lm(pEffComp ~ pPSRServices+ I(pPSRServices^2)+ pPlatWnA+ pIDV+ pPlatAir+ pVehSAC, data = MCClist)

summary(modelz)

screenreg(list(modelz))


```

**Automated Variable Selection: AIC**

``` {r echo=TRUE}
zfit <- lm(pEffComp ~ pPSRServices+ pPlatWnA+ pPlatEnC+ pIDV+ pPlatLand+ pPlatAir+ pPlatMnS+ pPlatVessel+ pPlatOther+ pRnD+ pPriceFixed+ pVehMAC+ pVehSAC+ pPscAir+ pPscLand+ pPscMnS+ pPscEngines+ pPscShips+ pPscFRSnC+ pPscPAMS+ pPscOther, data = MCClist)

step(zfit)

AIC(zfit)

afit <- lm(formula = pEffComp ~ pPSRServices + pPlatWnA + pPlatEnC + pPlatLand + pPlatMnS + pPlatVessel + pPlatOther + pRnD + pPriceFixed + pVehMAC + pVehSAC + pPscAir + pPscLand + pPscShips, data = MCClist)

screenreg(list(afit, modelz))


----------------------------------------------------------------
ggplotRegression <- function (fit) {

require(ggplot2)

ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "green") +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}

ggplotRegression(zfit)

ggplotRegression(afit)


```
